%----------------------------------------------------------------------------------------
%	PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\usepackage{graphicx} % Required for the inclusion of images
\usepackage{natbib} % Required to change bibliography style to APA
\usepackage{amsmath} % Required for some math elements 

\bibliographystyle{unsrtnat}

\setlength\parindent{0pt} % Removes all indentation from paragraphs

\renewcommand{\labelenumi}{\alph{enumi}.} % Make numbering in the enumerate environment by letter rather than number (e.g. section 6)

%\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------


\begin{document}

\begin{Large}
Lappeenrannan teknillinen yliopisto\\
School of Business and Management
\\\\\\\\\\\\\\\\\\\\\
Software Development Skills\\\\
\textbf{Johannes Hölker, Studentnumber: 609983}\\\\\\\\
\textbf{LEARNING DIARY\\ SOFTWARE DEVELOPMENT SKILLS\\ FULL STACK\\MODULE}
\end{Large}

\newpage 


\tableofcontents

\newpage

\section{20.10.2020} 
Dear Diary,\\
After reading the introduction of the course, I replicated the Word Template for the diary in \LaTeX using Texmaker as a GUI for writing. I managed finding my old Github Account then and installed Git on my Ubuntu system. I decided using Fork for my version control because I used it before and I am familiar with the program.
\section{22.10.2020}
I wanted to download Fork but I realised that Fork (and SourceTree) don't have a Linux Version. During watching the Introduction to Version Control I saw that the code editor Atom has an implemented version control GUI, so I decided to take that one.\\
Afterwards I watched the video about Node.js. Because I planned improving my Python skills this semester I realised that the course is made for JavaScript, which I didn't use before so it is a whole new challenge for me. Regarding the point that JavaScript is useful for sending/getting data from a server, I am looking forward to it.\\
I already have an idea for a JS application. With a friend of mine I was planning to make a simple ToDo-list application using the Python. For storing (and checking) the entries of the list on a server, I am thinking about using JavaScript.\\
Now I am setting up my Git-Repository and placing the Texmaker-Workspace in there. I tested the first commit of the folder $SD_FS$ in the command line and the second commit directly using the extension of Atom. During this I am getting familiar with the code editor Atom and the Github implementation in it.
\section{26.10.2020}
During watching the video about Node.js I am creating my Exercises Workspace and the Project Workspace in my project folder. 
After I tried isntalling Node.js by using the tar.xz folder, which i didn't managed, I nstalled it using the command:\\
sudo apt install nodejs\\
After doing so I realised that I installe the version 10.19. So I deinstalled the program and installed it using PPA. It didn't work either. So I used the version manager by tyoing the following commands:\\
$curl -sL https://raw.githubusercontent.com/creationix/nvm/v0.31.0$
$install.sh -o install_nvm.sh$\\
$bash install_nvm.sh$\\
nvm install 12.19.0\\
And setting the version to default.

\section{27.10.2020} 
My environment during the Node.js Crashcourse contains now Atom and my Linux Terminal and it works all fine while the exercise till I wanted to use quotes in a String. The quotes with the dollarsign were not recognised as a quote. I started looking it uo and also started the JavaScript course on Codecadamy for learning the Basics of JS.\\
I figured out that I used the wrong quotation marks. Using the ones from the video my quotes are working fine.\\
In the end of the Youtube video I made myself a Heroku account and got my first Website online. It was really exciting and I am looking forward to my project now. You can see the result following this link:\\
https://blooming-fjord-46718.herokuapp.com/\\
After finishing the video I made a Commit on Github.


\pagebreak 
%\bibliography{sample}
\end{document}